Gem-DeCan Figures

### 2021-12-01 Figures/Paper_Figures_final.Rmd
Add files via upload

myeloma_all_signs["Mean", ] = colMeans(myeloma_all_signs, na.rm = T) %>% round(., 3)
myeloma_all_signs_p["Mean", ] = colMeans(myeloma_all_signs_p, na.rm = T)
```

@@

Melanoma_GSE72056_all_signs["Mean", ] = colMeans(Melanoma_GSE72056_all_signs, na.rm = T) %>% round(., 3)
Melanoma_GSE72056_all_signs_p["Mean", ] = colMeans(Melanoma_GSE72056_all_signs_p, na.rm = T)
```

@@

                               "EpiDISH (BPRNACan)" = c(cor.test(meta$Epidish_BPRNACan_B, meta_facs$Bcells)$p.value, cor.test(meta$Epidish_BPRNACan_NK, meta_facs$NKcells)$p.value,

@@

                               "EpiDISH (BPRNACanProMet)" = c(cor.test(meta$Epidish_BPRNACanProMet_B, meta_facs$Bcells)$p.value, 

@@

                               "EpiDISH (BPRNACan3DProMet)" = c(cor.test(meta$Epidish_BPRNACan3DProMet_B, meta_facs$Bcells)$p.value,

@@

                               "EpiDISH (Melanoma)" = c(cor.test(meta$Epidish_CBSX.melanoma_B.cells, meta_facs$Bcells)$p.value,

@@

                               "EpiDISH (HNSCC)" = c(cor.test(meta$Epidish_CBSX.HNSCC_B.cell, meta_facs$Bcells)$p.value,

@@

                               "EpiDISH (NSCLC)" = c(cor.test(meta$Epidish_CBSX.NSCLC_B.cells, meta_facs$Bcells)$p.value,

@@

Melanoma_GSE93722_all_signs["Mean", ] = colMeans(Melanoma_GSE93722_all_signs, na.rm = T) %>% round(., 3)
Melanoma_GSE93722_all_signs_p["Mean", ] = colMeans(Melanoma_GSE93722_all_signs_p, na.rm = T)
```

>>>>

myeloma_all_signs$Mean = rowMeans(myeloma_all_signs, na.rm = T) %>% round(., 3)
myeloma_all_signs_p$Mean = rowMeans(myeloma_all_signs, na.rm = T)

myeloma_all_signs = myeloma_all_signs[order(myeloma_all_signs$Mean, decreasing = T), ]
myeloma_all_signs_p = myeloma_all_signs_p[rownames(myeloma_all_signs), ]
```

@@

Melanoma_GSE72056_all_signs$Mean = rowMeans(Melanoma_GSE72056_all_signs, na.rm = T) %>% round(., 3)
Melanoma_GSE72056_all_signs_p$Mean = rowMeans(Melanoma_GSE72056_all_signs_p, na.rm = T)

Melanoma_GSE72056_all_signs = Melanoma_GSE72056_all_signs[order(Melanoma_GSE72056_all_signs$Mean, decreasing = T), ]
Melanoma_GSE72056_all_signs_p = Melanoma_GSE72056_all_signs_p[rownames(Melanoma_GSE72056_all_signs), ]
```

@@

                               "EpiDISH BPRNACan" = c(cor.test(meta$Epidish_BPRNACan_B, meta_facs$Bcells)$p.value, cor.test(meta$Epidish_BPRNACan_NK, meta_facs$NKcells)$p.value,

@@

                               "EpiDISH BPRNACanProMet" = c(cor.test(meta$Epidish_BPRNACanProMet_B, meta_facs$Bcells)$p.value, 

@@

                               "EpiDISH BPRNACan3DProMet" = c(cor.test(meta$Epidish_BPRNACan3DProMet_B, meta_facs$Bcells)$p.value,

@@

                               "EpiDISH Melanoma" = c(cor.test(meta$Epidish_CBSX.melanoma_B.cells, meta_facs$Bcells)$p.value,

@@

                               "EpiDISH HNSCC" = c(cor.test(meta$Epidish_CBSX.HNSCC_B.cell, meta_facs$Bcells)$p.value,

@@

                               "EpiDISH NSCLC" = c(cor.test(meta$Epidish_CBSX.NSCLC_B.cells, meta_facs$Bcells)$p.value,

@@

Melanoma_GSE93722_all_signs$Mean = rowMeans(Melanoma_GSE93722_all_signs, na.rm = T) %>% round(., 3)
Melanoma_GSE93722_all_signs_p$Mean = rowMeans(Melanoma_GSE93722_all_signs_p, na.rm = T)

Melanoma_GSE93722_all_signs = Melanoma_GSE93722_all_signs[order(Melanoma_GSE93722_all_signs$Mean, decreasing = T), ]
Melanoma_GSE93722_all_signs_p = Melanoma_GSE93722_all_signs_p[rownames(Melanoma_GSE93722_all_signs), ]
```
